Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-07-14 paper.tex
Update paper.tex

%\gmj{I am not seeing the reason behind splitting this up in into two paragraphs.  I'll try reformatting the same information below:}

Research has so far shown that adaptive crop-wild introgression has played a significant role in the domestication and dispersal of many agronomically-important crops.
However, the dynamics of this process are not yet fully understood in the context of individual cases, and many questions remain.
At what taxonomic scale does introgression occur?
What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
When do species become so diverged that introgression is either maladaptive or impossible?
To what extent does the level of introgression across taxa depend on divergence time and/or mutation load between donor and recipient taxa? \gmj{I think we could include (effective) population size in this list of factors that determine extent of introgression.}
At what geographic scale does adaptive introgression occur? Is introgression generally restricted to very local populations, or does it pervasive over broad geographic ranges?
At what geographic scale is introgression adaptive?  Is it very local?  Does one see different architectures of introgression across different regions?
To what extent does this depend on the slope of environmental gradients, such as temperature, precipitation, and elevation, across these ranges?

\subsection*{Applied:}
Our identification and understanding of introgression in agroecosystems would be augmented by the development of wild relative genomic resources (annotated genomic sequence assemblies and functional genomic data sets \cite{huang2012}).
Additional study of introgression in agroecosystems could lead to advances in both basic and applied genetics, and specifically the continued improvement of modern crops.
Loci underlying the domesticated phenotype can be more clearly identified by removing the confounding population genetic signal of introgression.
These loci are potentially beneficial targets for crop improvement.
Furthermore, adaptive introgression that is clearly tied to a specific environment may include beneficial alleles that can be utilized in crop breeding.
\gmj{I could here include a handfull of examples of crops that farmers have bred adaptive alleles into.}

>>>>

%\gmj{I am not seeing the reason behind splitting this up in into these two paragraphs.  I'll try reformatting the same information below:}

Research has so far shown that adaptive crop-wild introgression has played a significant role in the domestication and dispersal of many agronomically-important crops.
However, the dynamics of this process are not yet fully understood, especially in the context of individual case examples, and many questions remain.

What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
After the hybrization events that lead to introgression, how long might the detectable genomic signals of introgression persist?

At what taxonomic scale does introgression occur?
When do species become so diverged that introgression is either maladaptive or impossible (due to  Dobzhansky-Muller incompatiblities or other mechanisms)?
To what extent does the level of introgression across taxa depend on divergence time and/or mutation load between donor and recipient taxa? \gmj{I think we could include (effective) population size in this list of factors that determine extent of introgression.}

Does one see different architectures of introgression across different regions?
Have introgressed alleles been constrained to the population which initially recieved the introgression, or have those alleles spread to the rest of of the crop species?
Is introgression generally restricted to very local populations, or does it pervasive over broad geographic ranges?
At what geographic scale is introgression adaptive?
To what extent does this depend on the slope of environmental gradients such as temperature, precipitation, and elevation across these ranges?

\subsection*{Applied:}
Our identification and understanding of introgression in agroecosystems would be augmented by the development of wild relative genomic resources, such as annotated genomic sequence assemblies and functional genomic data sets \cite{huang2012}.
Additional study of introgression in agroecosystems could lead to advances in both basic and applied genetics, and specifically the continued improvement of modern crops.
Loci underlying the domesticated phenotype can be more clearly identified by removing the confounding population genetic signal of introgression.
These loci are potentially beneficial targets for crop improvement.
Furthermore, adaptive introgression that is demonstrably tied to a specific environment may include beneficial alleles that can be utilized in crop breeding.
\gmj{I could here include a handfull of examples of crops that farmers have bred adaptive alleles into.}
